Visualization tool for comparison of amino acids in protein simulations

### 2017-06-29 paper/paper.tex
paper

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Visualization tool for comparison of mutations in protein simulations}

@@

\begin{abstract}
With the recent evolution of certain applications, there is a growing need for methods of this kind\ldots{}

This paper proposes exactly the right solution for this sub-problem in terms of several criterions. It introduces techniques for this and that tasks, improving this characteristic of the results. It further opens to a wider range of applications, as the experiments related in this paper confirms.

@@

%==========================================
\section{Introduction}
%
In the general context of this field, a certain kind of application has recently aggregated values for the following reasons.
%
However, existing approaches to produce good results for this application do not perform optimally yet, being limited to certain aspects and requiring too much resources to be actually used.

\subsection{Related work}
%
We can roughly classify the approaches used for our application in three categories: first category, second category, and last category.\\
Approaches in the first category were introduced by Pierre~\cite{Sibgrapi2015} using this and that techniques.

@@

\paragraph*{DSSP}
%
The first experiment checks this aspect of our method on perfect examples.

\paragraph*{SASA}
%
The first experiment checks this aspect of our method on perfect examples.

\paragraph*{GYRATE}
%
The first experiment checks this aspect of our method on perfect examples.

\paragraph*{ENERGY}
%
The first experiment checks this aspect of our method on perfect examples.

\paragraph*{RMSF}
%
The first experiment checks this aspect of our method on perfect examples.

@@

%==========================================
\section{Experiments}
%
We validate our technique through a series of experiments.

%==========================================
\section{Results and Discussion}
%
We performed the above-mentioned experiments on the following type of data: \ldots{} For each data, we used the following tuning parameters of our method.

\begin{table}
\caption{Performances results: timings are expressed in milliseconds.}
\label{tab:perfs}
\centering
\begin{tabular}{lr|rr|c}
\multicolumn{1}{c}{\bf Data} &
\multicolumn{1}{c|}{\bf Size} &
\multicolumn{1}{c}{\bf Ours} &
\multicolumn{1}{c|}{\bf Previous} &
\multicolumn{1}{c}{\bf Gain} \\ \hline
Data 1	&        50 	& 0.1 &     1 000	& x$10^3$ \\
Data 2	&      100 	& 0.2 &     2 000	& x$10^3$ \\
Data 3	&      500 	& 0.8 &   10 000	& x$10^3$ \\
Data 4	&   1 000 	& 1.2 &   20 000	& x$10^3$ \\
Data 5	&   5 000 	& 1.9 & 100 000	& x$10^4$ \\
Data 6	& 10 000 	& 2.1 & 200 000	& x$10^4$
\end{tabular}
\end{table}
%
%------------------------------------------------------------------------- 
\subsection{Performances}
%
We report on Table~\ref{tab:perfs} the performances of our technique on a computer at xxGhz with this graphic card.
We observe that our technique outperforms previous approaches on this kind of data, and an equivalent result on this other kind of data.

\subimages[htb]{Quality assessment}{quality}{
  \subimage{.48}{sibgrapi}%
  \subimage{.48}{sibgrapi}%
}

%------------------------------------------------------------------------- 
\subsection{Quality}
%
As observed on \figref{quality}, our method achieve good results in this situation. 
This can be measured by this criterion, and the results are reported on Table~\ref{tab:quality}.

\begin{table}
\caption{Quality measures: timings are expressed in milliseconds.}
\label{tab:quality}
\centering
\begin{tabular}{l|r|r}
\multicolumn{1}{c}{\bf Images} &
\multicolumn{1}{c|}{\bf PSNR} &
\multicolumn{1}{c}{\bf  MSE} \\ \hline
Image 1	&  40.2	& 0.02 \\
Image 2	&  30.9	& 1.02 \\
Image 3 &  20.1 & 0.18 \\
\end{tabular}
\end{table}

%------------------------------------------------------------------------- 
\subsection{Future work}
%
As mentioned in Section~\ref{sec:technique}, we expect our method to suit better this kind of data. On the other kind, this particularity does not fit into our formulation for this and that reason. Indeed, this can be observed in the results of \figref{quality}. 
We plan to improve for that kind of data in future work. However, our technique performed well on this data, which does not respect our condition, since this other aspect reduced the negative impact of its characteristic.

%==========================================
\section{Conclusion}
%
In this paper, we introduced this technique and showed that it is particularly appropriate for that application. We obtained this and that improvements, and plan to extend this application in that direction in future work.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Visualization tool for comparison of amino acids in protein simulations}

@@

\begin{abstract}

@@

%==========================================
\section{Introduction}
%

\subsection{Related work}
%

@@

\paragraph*{DSSP}
%

\paragraph*{SASA}
%

\paragraph*{GYRATE}
%

\paragraph*{ENERGY}
%

\paragraph*{RMSF}
%

@@

%==========================================
\section{Experiments}
%

%==========================================
\section{Results and Discussion}
%

%

%------------------------------------------------------------------------- 
\subsection{Future work}
%

%==========================================
\section{Conclusion}
%
